A Phenomenological Model for the Intra-Cluster Medium that matches X-ray and Sunyaev-Zel'dovich observations

### 2013-07-03 paper1.tex
New SZ Scaling Relation

\begin{figure*} 
\centering
\includegraphics[width=0.33\textwidth]{figures/lx_m.eps}
\includegraphics[width=0.33\textwidth]{figures/yx_m.eps}
\includegraphics[width=0.33\textwidth]{figures/sz_m.eps}
\caption{X-ray and SZ scaling relations. Grey triangles show the MultiDark
  sample (limited to the mass range covered by observations), the black line is
  the corresponding scaling relation, and the blue line is the
  observational result. The black crosses represent the median values of the
  quantity in question for a given mass bin (indicated by horizontal error
  bars), and the vertical error bars represent the standard deviation within a
  bin.  \emph{Left.} We compare the bolometric X-ray luminosity-to-mass
  relation, $L_{\rmn{bol}}-M_{500}$, at $z=0.2$ to the observational sample by
  \protect\cite{2010MNRAS.406.1773M} with a median of $z \approx 0.2$. \emph{Center.}
  $Y_{\rmn{X}}-M_{500}$ scaling relation of our model in comparison to the
  observational sample by \protect\cite{2010MNRAS.406.1773M}. \emph{Right.}
  $Y_{\rmn{SZ}}-M_{500}$ scaling relation at $z=0.16$ in comparison
  to the observational sample by the \protect\cite{2013arXiv1303.5080P} with a median
  redshift of about $0.15$. The bottom panels show the relative difference to
  the observational scaling relations.}
\label{fig:X_LM}
\end{figure*}

@@

In the right panel of Fig.~\ref{fig:X_LM}, we compare the
$Y_{\rmn{SZ}}-M_{500}$ relation in our model (calculated as in equation~(3) of
\citealp{2011arXiv1109.3709B}) with the observed scaling relation by the
\cite{2013arXiv1303.5080P}. {\bf We compare with the result obtained from the \emph{Planck} Cosmo 
sample with Malmquist bias correction (see their Table~A.1).} Their sample contains clusters 
up to $z \approx 0.45$ and has a median of $z \approx 0.15$; hence, we compare the data to our
relation at the MultiDark snapshot $z=0.16$ (that contains 11419 clusters above
our mass cut) which however is not used throughout the rest of the work. Our
model reproduces the data remarkably well, except for the high-mass end where
our simulations have a weaker constraining power due to the smaller box size in
comparison to the survey volume of {\em Planck}.  We find a scatter of
$\sigma_{yx} \approx 0.11$ which compares well with the \emph{Planck} result of
$\sigma_{yx} \approx 0.08$. In Table~\ref{tab:YSZfits}, we report our SZ scaling
relations for different redshifts.

@@

\begin{table} 
\begin{center}
\caption{$Y_{\rmn{SZ}, 500}-M_{500}$ scaling relations.}
\medskip
\begin{tabular}{cccc}
\hline
\phantom{\Big|}
redshift $z$ & $A$ & $B$ & $\sigma_{yx}$ \\
\hline\\[-0.5em]
 0      & $-27.93\pm0.07$ & $1.60\pm0.01$ & 0.109\\
 0.1   & $-27.74\pm0.07$ & $1.59\pm0.01$ & 0.109\\
 0.16 & $-27.76\pm0.08$ & $1.59\pm0.01$ & 0.109\\
 0.2   & $-27.65\pm0.08$ & $1.59\pm0.01$ & 0.109\\ 
 0.4   & $-27.57\pm0.10$ & $1.59\pm0.01$ & 0.108\\ 
 0.61 & $-27.50\pm0.13$ & $1.59\pm0.01$ & 0.109\\ 
 0.78 & $-27.15\pm0.18$ & $1.58\pm0.01$ & 0.109\\ 
 1      & $-27.01\pm0.26$ & $1.58\pm0.02$ & 0.109\\[0.5em] 
\hline
\end{tabular}
\label{tab:YSZfits}
\end{center}
\footnotesize{Note. Scaling relations are reported in the form of $\log_{10}~(E(z)^{-2/3}~Y_{\rmn{SZ},500}~/~h_{70}^{-2.5}~\rmn{Mpc}^{2})=A+B~\log_{10}~(M_{500}~/~h_{70}^{-1}~\rmn{M_{\odot}})$. The relation scatter $\sigma_{yx}$ is also shown.}
\end{table}

>>>>

\begin{figure*} 
\centering
\includegraphics[width=0.33\textwidth]{figures/lx_m.eps}
\includegraphics[width=0.33\textwidth]{figures/yx_m.eps}
\includegraphics[width=0.33\textwidth]{figures/sz_m.eps}
\caption{X-ray and SZ scaling relations. Grey triangles show the MultiDark
  sample (limited to the mass range covered by observations), the black line is
  the corresponding scaling relation, and the blue line is the
  observational result. The black crosses represent the median values of the
  quantity in question for a given mass bin (indicated by horizontal error
  bars), and the vertical error bars represent the standard deviation within a
  bin.  \emph{Left.} We compare the bolometric X-ray luminosity-to-mass
  relation, $L_{\rmn{bol}}-M_{500}$, at $z=0.2$ to the observational sample by
  \protect\cite{2010MNRAS.406.1773M} with a median of $z \approx 0.2$. \emph{Center.}
  $Y_{\rmn{X}}-M_{500}$ scaling relation of our model in comparison to the
  observational sample by \protect\cite{2010MNRAS.406.1773M}. \emph{Right.}
  $Y_{\rmn{SZ}}-M_{500}$ scaling relation at $z=0.18$ in comparison
  to the observational sample by the \protect\cite{2013arXiv1303.5080P} with a 
  median redshift of $0.18$. The bottom panels show the relative difference to
  the observational scaling relations.}
\label{fig:X_LM}
\end{figure*}

@@

In the right panel of Fig.~\ref{fig:X_LM}, we compare the
$Y_{\rmn{SZ}}-M_{500}$ relation in our model (calculated as in equation~(3) of
\citealp{2011arXiv1109.3709B}) with the observed scaling relation by the
\cite{2013arXiv1303.5080P}. {\bf We compare with the result obtained from the 
\emph{Planck} Cosmo sample with Malmquist bias correction (see their Table~A.1),
which has a median redshift of $0.18$. Hence, we compare the data to our relation 
at the MultiDark snapshot $z=0.18$ (that contains 11105 clusters 
above our mass cut) which however is not used throughout the rest of the work}. Our
model reproduces the data remarkably well, except for the high-mass end where
our simulations have a weaker constraining power due to the smaller box size in
comparison to the survey volume of {\em Planck}.  We find a scatter of
$\sigma_{yx} \approx 0.11$ which compares well with the \emph{Planck} result of
$\sigma_{yx} \approx 0.08$. In Table~\ref{tab:YSZfits}, we report our SZ scaling
relations for different redshifts.

@@

\begin{table} 
\begin{center}
\caption{$Y_{\rmn{SZ}, 500}-M_{500}$ scaling relations.}
\medskip
\begin{tabular}{cccc}
\hline
\phantom{\Big|}
redshift $z$ & $A$ & $B$ & $\sigma_{yx}$ \\
\hline\\[-0.5em]
 0      & $-27.93\pm0.07$ & $1.60\pm0.01$ & 0.109\\
 0.1   & $-27.74\pm0.07$ & $1.59\pm0.01$ & 0.109\\
 0.18 & $-27.73\pm0.08$ & $1.59\pm0.01$ & 0.109\\
 0.2   & $-27.65\pm0.08$ & $1.59\pm0.01$ & 0.109\\ 
 0.4   & $-27.57\pm0.10$ & $1.59\pm0.01$ & 0.108\\ 
 0.61 & $-27.50\pm0.13$ & $1.59\pm0.01$ & 0.109\\ 
 0.78 & $-27.15\pm0.18$ & $1.58\pm0.01$ & 0.109\\ 
 1      & $-27.01\pm0.26$ & $1.58\pm0.02$ & 0.109\\[0.5em] 
\hline
\end{tabular}
\label{tab:YSZfits}
\end{center}
\footnotesize{Note. Scaling relations are reported in the form of $\log_{10}~(E(z)^{-2/3}~Y_{\rmn{SZ},500}~/~h_{70}^{-2.5}~\rmn{Mpc}^{2})=A+B~\log_{10}~(M_{500}~/~h_{70}^{-1}~\rmn{M_{\odot}})$. The relation scatter $\sigma_{yx}$ is also shown.}
\end{table}
